I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-05 Paper/Paper_noProof.tex
intro

\begin{abstract}
  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc. Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN. This allows e.g. to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
  In the most recent years, the focus has been on combining several of these efficient techniques to optimize the speed/accuracy trade-offs (branch and bound, multi neuron encoding, milp encoding). While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools, 
  some smaller DNNs (hundreds of neurons) are still paradoxally challenging to address with efficient algorithms.

  In this paper, we analyze efficient DNNs algorithm based on abstraction (DeepPoly, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely compensation. Intuitively, a compensation happens when there are 2 paths 
   Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy.
\end{abstract}

@@

@@

The characteristic is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative. This is key reason why fast approximation like LP cannot get the exact upper and lower bounds.

If both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.

The general formal definition of compensating pair is as follows:

@@

	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes that goes consecutively through each layer. We call the first node source node and the last node target node.

@@

	3. A \emph{compensating pair} is a pair of paths with the same source node and target node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).

@@

The following theorem shows the meaning of compensating pairs:

@@

In this subsection, we will introduce the method to choose open nodes for MILP model by compensating pairs.

>>>>

\begin{abstract}
  Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formaly  that they are correct, with an annual competition to compare them, etc. Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN. This allows e.g. to check local robustness around an input $I$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $I$.
  In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs. While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern tools, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.

  In this paper, we analyze efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programing, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}. Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other. It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions. Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes. These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.
\end{abstract}

@@

Complexity

This paper does not focuss on producing the most efficient tool, and we did not spend engeenierial effort to optimize it. The focus is instead on the novel notion of compensation, the associated methodology and its evaluation. For instance, our implementation is fully in Python, with uncompetitive runtime for our DeepPoly implementation ($\approx 100$ slower than in $\beta$-CROWN). Still, evaluation of the methodology versus even the most efficient tools reveal a lot of potential for the notion of compensation, opening up several opportunities for applying it in different contexts of DNN verification.

@@

The key point is that, the products of all weights in the paths, have two different signs: along $bc$, the product is (strictly) positive, while along $b'c'$, the product is (strictly) negative.

But if both pairs are negative or positive, LP or even Interval Arithmetic will get the exact values of lower and upper bounds.

The definition of compensating pair is as follows:

@@

	1. A path is a sequence of nodes $\langle a,b,c,d,e,\cdots\rangle$ of nodes from one layer by one layer. We call the first node source node and the last node target node.

@@

	3. A compensating pair is a pair of path with the same starting node and end node, such that the two paths have no common node, and the values of two paths have opposite signs (one is strictly positive and another is strictly negative).

@@

To explain the of meaning of compensating pair, we introduce the following theorems about Diamond:

@@
